%-------------------------
% Resume in Latex
% Author : Shreyas Thakur
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Shreyas Thakur} \\ \vspace{1pt}
    \small +91 9937384867 $|$ \href{mailto:thakursm11@gmail.com}{\underline{thakursm11@gmail.com}} $|$
    \href{https://www.linkedin.com/in/shreyasthakur11/}{\underline{linkedin.com/in/shreyasthakur11}} $|$
    \href{https://ShreyasThakur11.github.io}{\underline{Website: ShreyasThakur11.github.io}} \\
    \small Thane, Maharashtra, India -- 400601
\end{center}


%-----------SKILLS & COMPETENCIES-----------
\section{Skills \& Competencies}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Business \& Analytical}{: Financial Accounting, Data Analysis, Process Optimization, Operations Management, Risk Assessment, Compliance, Feasibility Studies} \\
     \textbf{Tools \& Technologies}{: MS Excel (Advanced), Power BI, Python, MATLAB, AutoCAD, Aspen HYSYS, SQL}
    }}
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Management (IIM), Mumbai}{Mumbai, India}
      {Master of Business Administration (MBA)}{Jun 2026 -- Present}
    \resumeSubheading
      {Institute of Chemical Technology (ICT), Mumbai}{Mumbai, India}
      {Bachelor of Technology (B.Tech.) -- Chemical Engineering $|$ CGPA: 6.60/10.00}{2021 -- 2025}
      \resumeItemListStart
        \resumeItem{Acquired strong analytical and quantitative foundations through rigorous coursework in systems optimization, process modeling, and advanced mathematical concepts.}
        \resumeItem{Secured an aggregate of 85.67\% in Higher Secondary Certificate and 85.20\% in Secondary School Certificate examination.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tax \& Audit Assistant}{Jun 2025 -- May 2026}
      {Office of Santosh S. Bakshetti (Tax Consultant \& Auditor)}{Thane, Maharashtra, India}
      \resumeItemListStart
        \resumeItem{Assisted in auditing cooperative housing societies, verifying accounting entries and performing ledger scrutiny to identify documentation inconsistencies under strict confidentiality.}
        \resumeItem{Maintained accounts and recorded bookkeeping transactions for a manufacturing company, supporting reconciliation activities and organizing vital financial documentation systematically.}
        \resumeItem{Prepared tax filing inputs and collected financial data for individuals, verifying information accuracy to support timely income tax compliance.}
      \resumeItemListEnd

    \resumeSubheading
      {In-Plant Trainee -- Process Engineering}{Jun 2024 -- Aug 2024}
      {Epigral Ltd. (Formerly Meghmani Finechem)}{Dahej, Gujarat, India}
      \resumeItemListStart
        \resumeItem{Analyzed operational data to perform root cause analysis on catalyst deactivation, establishing a predictive monitoring framework for enhanced lifecycle management.}
        \resumeItem{Investigated recurring burner failures through process safety management protocols, proposing structured corrective actions to minimize operational downtime and safety risks.}
        \resumeItem{Conducted a systematic moisture reduction study in purification systems, identifying critical operational bottlenecks to optimize process efficiency and product quality.}
        \resumeItem{Monitored continuous chemical manufacturing operations via distributed control systems, managing real time process parameters to maintain stability and safety compliance.}
        \resumeItem{Trained in hazard and operability studies, permit systems, and change management documentation to ensure rigorous compliance with industrial safety protocols.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Plant Design -- Ambrettolide Manufacturing (25 TPA)} $|$ \emph{Capstone}}{Sep 2024 -- Apr 2025}
          \resumeItemListStart
            \resumeItem{Designed an end to end chemical manufacturing facility, evaluating three distinct synthesis pathways through rigorous techno economic and process safety analyses.}
            \resumeItem{Performed detailed material and energy balance computations, executing quantitative equipment sizing for reactor, separation, and heat transfer systems.}
            \resumeItem{Developed process flow diagrams and piping layouts, conducting a hazard and operability study that identified fifteen operational deviation scenarios.}
            \resumeItem{Prepared comprehensive capital and operational expenditure estimates, conducting return on investment analysis and site layout planning for the facility.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Impact of Climate Change on Water Quality} $|$ \emph{Seminar}}{Nov 2024 -- Jan 2025}
          \resumeItemListStart
            \resumeItem{Analyzed the environmental impact of climate change on water resources, benchmarking system changes against national pollution control board standards.}
            \resumeItem{Evaluated advanced water purification methodologies, conducting scalability and feasibility assessments for municipal and industrial scale applications.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------LEADERSHIP & ACHIEVEMENTS-----------
\section{Leadership \& Achievements}
  \resumeItemListStart
    \resumeItem{Earned industrial certifications in environmental pollution management, petroleum refinery engineering, and industrial internet of things, ranking top five percent nationwide.}
    \resumeItem{Led creative initiatives for Bombay Technologist, managing editorial content and coordinating design operations as Creative Head for the official technical magazine.}
    \resumeItem{Secured second place in the entrepreneurship blueprint business plan competition, presenting a structured market feasibility study and financial projection model.}
  \resumeItemListEnd


%-------------------------------------------
\end{document}

